Enabling conditions for effective community-based marine reserves in small-scale fisheries

### 2018-03-20 docs/WSSFConf_abstract/Abstract_WSSFConf.Rmd
moved abstract to its own folde under docs

---
title: "Enabling conditions for effective community based marine reserves in small scale fisheries"
author: "Juan Carlos Villaseñor-Derbez$^{1,*}$, Eréndira Aceves-Bueno$^{1,*}$, Alvin Suarez-Castillo$^{2}$, Stuart Fulton$^{2}$, Jorge Torre$^{2}$"
date: "$^{1}$Bren School of Environmental Science and Management, University of California, Santa Barbara, Santa Barbara, CA, USA. $^{2}$Comunidad y Biodiversidad A.C.,  Guaymas, Mexico"
output: pdf_document
---

>>>>

---
title: "Enabling conditions for effective community-based marine reserves in small-scale fisheries"
author: "Juan Carlos Villaseñor-Derbez$^{1,*}$, Eréndira Aceves-Bueno$^{1,*}$, Alvin Suarez-Castillo$^{2}$, Stuart Fulton$^{2}$, Jorge Torre$^{2}$"
date: "$^{1}$Bren School of Environmental Science and Management, University of California, Santa Barbara, Santa Barbara, CA, USA. $^{2}$Comunidad y Biodiversidad A.C.,  Guaymas, Mexico"
output: pdf_document
---
